We present Thayer-Net, a controlled synthetic benchmark for galaxy deblending
with Galaxy10 DECaLS cutouts. The benchmark constructs foreground-only blends
with known target references, reducing rectangular artifacts from naive cutout
addition. We compare identity and threshold baselines with compact U-Net models
trained for direct target reconstruction, residual correction-field prediction,
balanced hard-case residual prediction, and affected/core-weighted residual
prediction. Thayer-Direct improves affected-region mean squared error over
identity on original development blends, but hard stress testing reveals weaker
robustness under stronger overlap and contaminant conditions. Thayer-Residual
improves stress performance by learning a blend-to-target field to subtract.
Thayer-BR v0.1 shows that balanced hard-case training improves robustness, and
Thayer-BR v0.2 Moderate further improves affected-region and core affected
error with a weighted residual loss. A duplicate-safe grouped retrain reaches
28.81x lower affected-region MSE than identity on grouped normal development
blends, 15.80x on hard stress, 9.18x on compact-bright stress, and 15.84x on
high-core-obstruction stress. The earlier row-index benchmark gave 32.3x and
19.6x normal/stress ratios; its duplicate implication had a minor measured
aggregate effect but violated source-independent protocol. These results are
development evidence, not a locked final or survey-grade claim, and remain
limited by display-RGB compositing, simplified sky/PSF/noise, target centrality,
source reuse, and apparent-size assumptions.
