The Thayer-Direct result shows that the controlled synthetic task is learnable:
learned reconstruction substantially improves affected-region error over
identity and threshold baselines. The hard stress test shows that normal
row-index development performance is not enough to characterize robustness.

Thayer-Residual helps because the model learns contaminant light to subtract
rather than redrawing the whole target. This can preserve target structure in
regions that are already correct in the blended image. Thayer-BR v0.1 helps
because core overlap and bright/similar-size contaminants are sampled
deliberately during optimization instead of appearing only by chance.
Thayer-BR v0.2 Moderate adds another improvement by placing more loss weight on
contaminated and affected target-core pixels, which better matches the primary
evaluation objective.

The exact-pixel/exact-coordinate grouped v0.2 retrain is now the current
source-group-disjoint development reference. The original checkpoint on grouped
manifests remains an exposure-confounded diagnostic, and the historical 32.3x
result remains original development evidence only. None of these is a final
paper estimate; a fresh untouched final source partition is still required.

The Strong weighting ablation is important because it shows that more weighting
is not automatically better. Stronger affected/core weights slightly improve
stress core affected MSE but worsen aggregate normal and stress affected MSE.
The Moderate setting is the best current balance.

The result should not be overstated. Thayer-Direct, Thayer-Residual, and
Thayer-BR v0.1 still win on some individual samples. Some failures involve
ambiguous overlap, target-core obstruction, over-smoothing, broad low-level
artifacts, or lost target detail. Also, high blend severity is not identical to
model difficulty: an obvious contaminant can be severe but easy to subtract,
while a small overlap can be hard if it destroys central target structure.

The size/visual audit found wide apparent contaminant/target size variation but
weak learned-model affected-error dependence on size ratio. This does not
invalidate the current result, but it motivates a future size-normalized
grouped development benchmark. The future untouched final pool must not be used
to design that benchmark. The halo-band audit improved in aggregate for v0.2 Moderate
relative to v0.1, while selected individual examples still show broad low-level
artifacts. Both aggregate metrics and visual counterexamples should be reported.

The current benchmark remains synthetic. More realistic sky backgrounds, PSF
variation, correlated source environments, apparent-size-controlled
evaluations, and survey-like noise are needed before making broader
astronomical claims.
