Evaluation reports whole-image MSE, MAE, PSNR, and SSIM, along with
affected-region MSE and MAE. Affected-region metrics are primary because most
pixels in each synthetic cutout are unchanged. The affected region is defined by
pixels where the blended image differs from the clean target by more than the
affected threshold after averaging absolute RGB differences.

The primary aggregation is the macro mean of per-sample metrics; auxiliary
micro values weight mask pixels. Empty regional masks are excluded with valid
counts reported. Clipped and unclipped reconstructions are evaluated
separately, and paired win rates require identical sample IDs.

The current development protocol groups exact pixel hashes and exact
coordinates before source assignment. Both target and contaminant remain inside
train, validation, or grouped development-test partitions, and all saved blend
and mask hashes replay exactly. This controls the known exact leakage but does
not prove exhaustive near-duplicate identity or provide an untouched final
partition.

The hard stress test uses 1,000 blends with maximum shift 18, brightness range
0.8 to 1.4, blur range 0.0 to 0.15, noise range 0.0 to 0.006, rotation off,
minimum size ratio 0.75, minimum affected mask fraction 0.01, and affected
threshold 0.02.

The analysis distinguishes generation difficulty, blend severity, target-core
obstruction, and model failure. Blend severity measures image-level damage, not
model difficulty. Model failure is measured by affected-region model error and
improvement relative to identity.

Several audits check whether the development result depends on a
fragile metric implementation. The affected mask was verified to use
$\mathrm{mean}_c(|X-Y|) > \tau$, independent of model prediction error. Mask
thresholds 0.005, 0.01, 0.02, and 0.04 were checked, along with dilation radii
0, 1, 3, 5, and 9 pixels for halo sensitivity. Residual sign logic was checked
by verifying that the residual target is $X-Y$ and reconstruction is
$X-\hat{R}$.

The original v0.2 Moderate result is also evaluated with a multi-seed audit, an
apparent-size audit, a centrality/core-obstruction audit, a halo-band error
audit, and visual-vs-metric disagreement examples. These audits are diagnostic:
they support careful interpretation but do not convert the controlled synthetic
benchmark into real-sky validation. The multi-seed audit varies blend-generation
and evaluation seeds, not independent training seeds.
